BERT Model Compression and Weight Sharing

### 2019-05-13 paper/paper.tex
Add todo on outside data
Removing abstract bullet points

\begin{abstract}
\raggedright
  \begin{itemize}
  \item We apply model compression techniques to fine-tuned BERT on multiclass
  classification problems.
  \item Knowledge distillation and DeepTwist-based compression techniques give
  us moderate compression benefits for a commensurate decrease in model
  performance.
  \item We achieve our most compelling results from employing the DeepTwist
  framework to share weights across BERT models fine-tuned for different tasks.
  \item Our work demonstrates most weights need not change in the fine-tuning
  process.
%   \item This document describes the expected style, structure, and rough
%   proportions for your final project write-up.
%   \item While you are free to break from this structure, consider it a strong
%   prior for our expectations of the final report.
%   \item Length is a hard constraint. You are only allowed max \textbf{8 pages}
%   in this format. While you can include supplementary material, it will not be
%   factored into the grading process. It is your responsibility to convey the
%   main contributions of the work in the length given.
  \end{itemize}

@@

\subsection{Deep Twist}

@@

\section{Methods}
In this section, we briefly discuss our experimental setup. We mostly
work with
SST-2, a binary sentiment classification task in the GLUE multitask benchmark
framework \citep{wang2018glue}. We also validate the model's
performance with trial on the Quora Question Pair (QQP) task, which is a
binary classification task for whether two questions are equivalent. We
train with a maximum sequence length of 64 and batch size of 32 on the
NC-6 and NC-12 virtual machines on Microsoft Azure. We use the basic 
\texttt{BERT-base-uncased} model for our experimental results. We employ
early stopping in training, with patience of 1 epoch, and early stopping is
guided by validation error.

@@

\begin{itemize}
\item What were the results comparing previous work / baseline systems / your
systems on the main task?
\item What were the secondary results comparing the variants of your system?
\item This section should be fact based and relatively dry. What happened, what
was significant?
\end{itemize}

@@

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
\caption{Training loss (left), val. loss (middle), and val. accuracy
(right) for LSTM KD}
\label{fig:kdlstmloss}
\end{figure*}

@@

>>>>

\begin{abstract}
% \raggedright
  We apply model compression techniques to fine-tuned BERT on multiclass
  classification problems.  Knowledge distillation and DeepTwist-based compression techniques give
  us moderate compression benefits for a commensurate decrease in model
  performance. We achieve our most compelling results from employing the DeepTwist
  framework to share weights across BERT models fine-tuned for different tasks. Our work demonstrates most weights need not change in the fine-tuning
  process.
%   \item This document describes the expected style, structure, and rough
%   proportions for your final project write-up.
%   \item While you are free to break from this structure, consider it a strong
%   prior for our expectations of the final report.
%   \item Length is a hard constraint. You are only allowed max \textbf{8 pages}
%   in this format. While you can include supplementary material, it will not be
%   factored into the grading process. It is your responsibility to convey the
%   main contributions of the work in the length given.
  % \end{itemize}

@@

\subsection{DeepTwist}

@@

\section{Methods}
In this section, we briefly discuss our experimental setup. We mostly
work with
SST-2, a binary sentiment classification task in the GLUE multitask benchmark
framework \citep{wang2018glue}. We also validate the model's
performance with trial on the Quora Question Pair (QQP) task, which is a
binary classification task for whether two questions are equivalent. We
train with a maximum sequence length of 64 and batch size of 32 on the
NC-6 and NC-12 virtual machines on Microsoft Azure. We use the basic 
\texttt{BERT-base-uncased} model for our experimental results. We employ
early stopping in training, with patience of 1 epoch, and early stopping is
guided by validation loss.

@@

We show our results in \Cref {tab:deeptwist_results,tab:kd_results}. In the top
pane of \Cref {tab:deeptwist_results}, we show the result of various
DeepTwist-based compression techniques on the sentiment classification task,
SST-2, stratifying by method and then by parameter of the method. Difference
pruning, pruning, and rank reduction are implemented as \emph{distortion by
layer} (see \Cref{sec:model}), where as ``difference pruning (global)''
indicates difference pruning, but pooling all parameter values from all layers.
The bottom pane of \Cref{tab:deeptwist_results} shows the performance on QQP of
some competitive-performing model setups on SST-2, which are all
difference-pruning based. In \Cref{tab:kd_results}, we present some knowledge
distillation experiments, with the student network being an LSTM or a CNN, with
or without dropout \citep{kim2014convolutional}.

For the most part, difference pruning seems to be robust to the pruning
rate. As a sanity check, we include difference pruning with 100\% pruning
rate, which is equivalent to BERT model without fine-tuning, and obtaining
essentially uniform results on the validation set. Difference pruning also
seems to outperform both ``first-order'' DeepTwist techniques, pruning and
rank reduction, which is unsurprising as difference pruning uses more
parameters and uses parameters that are pretrained. Difference pruning also
seems to extend to other tasks in GLUE, as it retains its behavior in
SST-2 to QQP, for the most part. Knowledge distillation seems less
promising. While knowledge distillation
slightly improves upon the model directly trained on data, it does not
fully replicate the performance of the teacher network. We now discuss our
results in detail.

% \begin{itemize}
% \item What were the results comparing previous work / baseline systems / your
% systems on the main task?
% \item What were the secondary results comparing the variants of your system?
% \item This section should be fact based and relatively dry. What happened,
% what was significant?
% \end{itemize}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\textwidth]{../figs/kd_lstm_training.png}
\caption{Training loss (left), val. loss (middle), and val. accuracy
(right) for LSTM KD}
\label{fig:kdlstmloss}
\end{figure*}

@@

@@

% TODO: talk about bringing in outside data for KD
